### 2020-05-29 paper.tex
Add CH Reference
Study Desgin

	\normalsize{
		Manuel Alabor\\
		Supervised by Prof. Dr. Markus Stolze\\
		\par
		\vspace{2ex}
		HSR University of Applied Sciences Rapperswil\\
		\par
		\vspace{2ex}
		\today{} (\version)
	}
	\par
	\vspace{2ex}

@@

Transcripts of informal interviews and ``war stories'' collected from multiple practitioners will give insight in the challenges they face in their day-to-day jobs. We will validate their statement in a controlled experiment and answer our first research question:

@@

@@

\begin{itemize}
	\item \emph{Hypothesis: If frontend engineers are given an RxJS-based problem, then they will modify the code in order to understand its behavior.}
\end{itemize}

>>>>

	\normalsize{
		Manuel Alabor\\
		Supervised by Prof. Dr. Markus Stolze\\
		\par
		\vspace{2ex}
		HSR University of Applied Sciences Rapperswil, Switzerland\\
		\par
		\vspace{2ex}
		\today{} (\version)
	}
	\par
	\vspace{2ex}

@@

Transcripts of informal interviews and ``war stories'' collected from multiple practitioners will give insight in the challenges they face in their day-to-day jobs. We will validate their statement in an observational study and answer our first research question:

@@

We explored on how engineers use RP and what techniques they might apply for debugging problems earlier. We observed that most participants tend to modify their source code manually with trace logs and alike in order to find underlying problems. It is further our own experience that this practice is often not a productive one since the evaluation of trace information, once available, can be cumbersome and time consuming. In addition, removing log statements after the debugging process might leave new bugs in production code if not done carefully. We identified this circumstance as one of the main debugging practices when software engineers work with RxJS-based code.

This is why we saw the need in validating earlier statements about manual code modification for debugging reasons with an observational study. Our study sought to validate following hypothesis:

\begin{itemize}
	\item \emph{Hypothesis: If software engineers are given an RxJS-based problem, then they will modify the code in order to understand its behavior.}
\end{itemize}

@@

The subjects for our study were required to have experience in developing applications with RxJS. We did not distinguish between frontend or backend engineers, hence in the end were able to find four subjects willing to participate in our experiment. We were interested to see how the subjects apply debugging techniques they would use in a common situation at their jobs. This is why we decided to conduct the experiment in a rather uncontrolled environment where the subjects used their own devices with their development environments of personal preference. Our objective for the experiment was communicated as broad as possible to prevent bias: ``We are interested in how \emph{you} debug a problem'' did not mention the hypothesis by intention.

We planned to have a one hour session for the actual experiment with each subject, followed-up by a short, unattended after-action survey. The experiment was executed in two consecutive blocks of 25 minutes each. We provided a ZIP file containing the source code for two frontend web applications implemented using TypeScript and RxJS along with a test suite at the start of the experiment. Each of these applications were rigged with two to three bugs which we asked the subjects to identify and fix using whatever debugging techniques they prefer and commonly use. A block was considered as complete once either the test suite signaled all bugs as resolved or the 25 minutes were exceeded. We asked our subjects to act like in a pair programming situation where they ``think out loud'' their thought process. We refrained to answer any question related to the ``where'' a bug has to be expected though.

A week before the actual experiment, we sent out the participant briefing document to all of our subjects. We outlined the course of action and provided them with an example ZIP file. This file contained the same setup as the file provided at the experiment and allowed the subjects to get accustomed with things like starting the web applications or running the test suites.

We decided to monitor our subjects progress remotely using voice chat and screen sharing due to the COVID-19 situation at the time of our study. This allowed us to record the sessions with relative low technical effort for later evaluation.

The quantitative after-action survey provided after the main part of the study was provided within 24 hours after a subjects participation. We asked the subjects about (i) the number of years they have experience with RxJS, (ii) if they currently use RxJS on or off their jobs, (iii) in which field (like frontend, backend or others) they use RxJS and finally (iv) which tools and techniques they use to debug RxJS-based code.

\subsection{Study Results}
